Poincar\'e--Friedrichs constants over triangulated domains

### 2024-06-21 main.tex
Update on Overleaf.

\begin{remark}
    Our main interest in this manuscript are finite triangulations of compact sets. 
    There is another reason why we insist on the triangulation being finite: 
    if we do not require our simplicial complexes to be finite,
    then our definition would be considerably more permissive than the typical definitions in topology. 
    % 
    For example, if we allowed simplicial complex to be infinite, 
    then any subset of Euclidean space would give rise to an ``infinite $0$-dimensional complex''. But this obviously does not reflect the topology. 
    %
    A more interesting such example is this:
    the Cantor set $\calC \subseteq [0,1]$ is a compact set 
    that underlies an ``infinite $0$-dimensional simplicial complex''.
    If we place $\calC$ on the x-axis of a 2D coordinate system 
    and connect each member of $\calC$ to $(0,1)$ via a straight line segment, 
    then the resulting set is still compact, even path-connected,  
    but has an ``infinite $1$-dimensional triangulation''.
    % 
    However, none of these infinite families are simplicial complexes in the sense of topology~\cite{spanier1966homology}. 
\end{remark}

@@

In the special case $p=2$, we always have $\| u - u_\Omega \|_{L^{2}(\Omega)} \leq \| u \|_{L^{2}(\Omega)}$ for any $v \in L^{2}(\Omega)$,
and therefore even $C_{\varnothing,\Omega,2} = C_{{\rm PF},\Omega,2}$. 
This follows from the orthogonality constant functions to average-free functions in $L^2(\Omega)$,
and it also follows from the projection estimate (see, e.g.,~\cite{xu2003some}).\footnote{\color{red}Is there a better name for this than Xu-Zikatanov estimate?}
Stern~\cite{stern2015banach} provided a generalization of the projection estimate that implies improved estimate for all $L^p$ spaces with $1 \leq p \leq \infty$:
since taking the average is a the projection onto the constants functions with unit norm, it now follows that 
\begin{align*}
    \| v - v_\Omega \|_{L^{p}(\Omega)}
    \leq 
    \min\left( 2, 2^{|2/p-1|} \right)
    \| v \|_{L^{p}(\Omega)}
    = 
    2^{|2/p-1|} 
    \| v \|_{L^{p}(\Omega)}
    ,
    \quad 
    v \in L^p(\Omega)
    .
\end{align*}
We have $1 \leq 2^{|2/p-1|} \leq 2$ for $1 \leq p \leq \infty$.
The upper bound is only attained in the limit cases $p = 1$ and $p = \infty$, and the lower bound is only attained if $p = 2$, which reproduces the improved estimate for the Hilbert space case.
The main consequence for us is the estimate 
$C_{\varnothing,\Omega,p} \leq 2^{|2/p-1|} C_{{\rm PF},\Omega,p}$.
We conclude that our notion of Poincar\'e--Friedrichs constant is equivalent to the notion of Poincar\'e constant in the literature, up to a numerical factor that only depends on $1 \leq p \leq \infty$.
\color{red} Question: can the estimate above be further improved for general $p$? Are there known results in the literature? \color{black}

There is yet another characterization of the Poincar\'e--Friedrichs inequality that we like to point out. 
We define the potential 
\begin{align*}
    \Phi( \bff ) := \argmin\limits_{ \substack{ v \in W^{1,p}(\Omega) \\ \nabla v = \bff } } \| v \|_{L^{p}(\Omega)},
    \quad 
    \bff \in \nabla W^{1,p}(\Omega)
    .
\end{align*}
Clearly, 
\begin{align*}
    \| \Phi(\bff) \|_{L^p(\Omega)} \leq C_{{\rm PF},\Omega,p} \| \bff \|_{L^p(\Omega)},
\end{align*}
and this inequality is sharp by definition of $\Phi$ provided that $C_{{\rm PF},\Omega,p}$ is smallest possible constant in \eqref{math:inequalitypf:gradient}. 
However, $\Phi : \nabla W^{1,p}(\Omega) \rightarrow L^p(\Omega)$ is generally a nonlinear operator for $p \neq 2$. 
Consequently, any linear potential operator $\overline\Phi : \nabla W^{1,p}(\Omega) \rightarrow L^p(\Omega)$
satisfying $\nabla \overline\Phi( \bff ) = \bff$ for any $\bff \in \nabla W^{1,p}(\Omega)$ must have an operator norm that obeys the lower bound 
\begin{align*}
    C_{{\rm PF},\Omega,p} 
    \leq 
    \argmin\limits_{ v \in \nabla W^{1,p}(\Omega) \setminus \bbR } 
    \frac{ \| \overline\Phi(\nabla v) \|_{L^p(\Omega)} }{ \| \nabla v \|_{L^p(\Omega)} }
    .
\end{align*}
A natural choice is the linear operator $\Phi_{\varnothing} : \nabla W^{1,p}(\Omega) \rightarrow L^p(\Omega)$ that satisfies 
\begin{align*}
    \Phi_{\varnothing}( \nabla u ) = u - u_{\Omega},
    \quad 
    u \in W^{1,p}(\Omega)
    .
\end{align*}
Its operator norm is just the smallest Poincar\'e constant $C_{\varnothing,\Omega,p}$.

In the light of these musings, we can clarify that our objective is the construction of linear potential operators for the gradient and later for the curl and divergence operators. 
Any Poincar\'e--Friedrichs inequality~\eqref{math:inequalitypf:gradient} is comparable to an upper bound for the generalized inverse of the gradient operator $\nabla : W^{1,p}(\Omega) \rightarrow L^{p}(\Omega)^{n}$. The potential reconstruction is the natural approach towards the topic when addressing the curl and divergence operators.

@@

We now collect examples for Poincar\'e--Friedrichs inequalities for important special cases; see also~\cite[Lemma~3.24]{ern2021finite} for a short overview. Over convex bounded domains, it is known~\cite{bebendorf2003note,acosta2004optimal} that 
\begin{align}\label{math:acostaduran}
    \| u - u_{\Omega} \|_{L^{1}(\Omega)}
    \leq 
    \frac{\diam(\Omega)}{2}
    \| \nabla u \|_{L^{1}(\Omega)}
    ,
    \quad 
    u \in W^{1,2}(\Omega)
    ,
    \\
    \| u - u_{\Omega} \|_{L^{2}(\Omega)} \label{math:bebendorf}
    \leq 
    \frac{\diam(\Omega)}{\pi}
    \| \nabla u \|_{L^{2}(\Omega)}
    ,
    \quad 
    u \in W^{1,2}(\Omega)
    .
\end{align}
These two estimates are the best possible in the cases $p=1$ and $p=2$, respectively, in terms of the diameter alone. 
Moreover, when $1 < p < \infty$, we know~\cite{chua2006estimates} that
\begin{align}\label{math:chuawheeden}
    \| u - u_{\Omega} \|_{L^{p}(\Omega)}
    \leq 
    C_{{\rm CW},p}
    \diam(\Omega)
    \| \nabla u \|_{L^{p}(\Omega)}
    ,
    \quad 
    u \in W^{1,p}(\Omega)
    ,
\end{align}
where 
\begin{align}
    C_{{\rm CW},p} 
    := 
    \sup\limits_{ v \in C^\infty([0,1]) \setminus \bbR } 
    \frac{ 
        \| v - v_{[0,1]} \|_{L^{p}([0,1])} 
    }{ 
        \| \nabla v \|_{L^{p}([0,1])} 
    }
    \leq 
    \sqrt[p]{p} 2^{1-\frac 1 p}
    =
    2
    \left( \frac p 2 \right)^{\frac 1 p}
    .
\end{align}
In addition to that,
according to~\cite{ferone2012remark,esposito2013poincare}, when $1 < p < \infty$, one can show that 
\begin{align}\label{math:esposito:pf}
    \min\limits_{ c \in \bbR }
    \| u - c \|_{L^{p}(\Omega)}
    \leq 
    C_{\rm{EFNT},p}
    \diam(\Omega)
    \| \nabla u \|_{L^{p}(\Omega)}
    ,
    \quad 
    u \in W^{1,p}(\Omega)
    ,
\end{align}
where 
\begin{align}
    C_{\rm{EFNT},p}
    :=
    \frac{ p \sin(\pi/p) }{ 2\pi \sqrt[p]{p-1} }
    .
\end{align}
The constant $C_{\rm{EFNT},p}$ is the best possible. 
Note that the last inequalities imply, again when $1 < p < \infty$, the Poincar\'e inequalities
\begin{align}\label{math:esposito:poincare}
    \| u - u_{\Omega} \|_{L^{p}(\Omega)}
    \leq 
    2^{|1-\frac 2 p|}C_{\rm{EFNT},p}
    \diam(\Omega)
    \| \nabla u \|_{L^{p}(\Omega)}
    ,
    \quad 
    u \in W^{1,p}(\Omega)
    .
\end{align}
The main feature in proving these results is that the best constant in the Poincar\'e inequality is already the constant in the $1$-dimensional case. 
Finally,
since convex domains are Lipschitz domains, we may estimate 
\begin{align}\label{math:lipschitzestimate}
    \min\limits_{ c \in \bbR }
    \| u - c \|_{L^{\infty}(\Omega)}
    \leq 
    \diam(\Omega)
    \| \nabla u \|_{L^{\infty}(\Omega)}
    ,
    \quad 
    u \in W^{1,\infty}(\Omega)
    .
\end{align}

@@

Given a gradient vector field, we can reconstructed the original scalar function up to a constant by a well-understood procedure: after fixing a starting point, we integrate the gradient vector field along lines emanating from that starting point. This defines a scalar potential. 
This shall be our inspiration for estimating the Poincar\'e constant over triangulated domains, which we achieve by an explicit construction of scalar potentials. 
After fixing a starting triangle, we construct a scalar potential for a given gradient vector field on larger and larger simplicial neighborhoods. This is achieved by a local patchwise construction of a potential and matching that local contribution to the global potential being constructed so far. 
Consequently, the overall estimate depends on the local Poincar\'e constants, the mesh quality, and the depth of the recursion.

@@

\begin{lemma}\label{lemma:volumecomparison}
    Let $T_1$ and $T_2$ be two $n$-simplices that share a common face $F$. Then 
    \begin{align*}
        \frac{ \vol(T_1) }{ \vol(T_2) }
        \leq 
        \frac{\diam(T_1)^n}{n! \cdot \vol(T_1)} 
        \cdot 
        \frac{\diam(T_2)^n}{n! \vol(T_2)} 
        .
    \end{align*}
\end{lemma}
\begin{proof}
    Let $h_1$ and $h_2$ be the heights of $F$ in the simplices $T_1$ and $T_2$, respectively. 
    Then $\vol(T_1) = h_1 \vol(F)/n$ and $\vol(T_2) = h_2 \vol(F)/n$, and thus $\vol(T_1)/\vol(T_2) = h_1/h_2$.
    We estimate 
    \begin{align*}
        h_1 &\leq \diam(T_1) \leq \frac{\diam(T_1)^n}{n! \cdot \vol(T_1)} \diam(F),
        \\
        h_2 &\geq n! \cdot \frac{\vol(T_2)}{\diam(T_2)^n} \diam(T_2) \geq n! \cdot \frac{\vol(T_2)}{\diam(T_2)^n} \diam(F)
        .
    \end{align*}
    The desired estimate follows. 
    % Together with analogous estimates that swap the roles of $h_1$ and $h_2$, we find 
    % \begin{align*}
    %     \max\left( \frac{h_1}{h_2}, \frac{h_2}{h_1} \right)
    %     \leq 
    %     \frac{\diam(T_1)^n}{n! \cdot \vol(T_1)} 
    %     \cdot 
    %     \frac{\diam(T_2)^n}{n! \vol(T_2)} 
    %     .
    % \end{align*}
\end{proof}

\begin{remark}
    Whenever $T$ is an $n$-dimensional simplex, the ratio $\diam(T)^n / \vol(T)$ measures the ``shape quality'' of a simplex and is instance of a so-called \emph{shape measure}. 
    This geometric ratio equals what is known as \emph{fatness} in differential geometry~\cite{cheeger1984curvature} and is precisely the reciprocal of the \emph{fullness} discussed by Whitney~\cite{whitney2012geometric}. 
    The \emph{thickness} of a simplex is the ratio of its smallest height to its diameter~\cite{munkres2016elementary}.
    Alternative shape measures have been used throughout the literature of numerical analysis and computational geometry to quantify the quality of simplices.
    One example, commonly referenced in finite element literature, is the ratio of the diameter and the radius of the largest inscribed circle of a simplex 
    (see~\cite[p.61, Definition 5.1]{braess2001finite}, ~\cite[p.97, Definition (4.2.16)]{brenner2008mathematical},~\cite[Definition~11.2]{ern2021finite}). 
\end{remark}

\begin{lemma}\label{lemma:poincarefriedrichsoverfacepatch}
    Suppose that $T, T'$ are two $n$-simplices whose intersection is a common face $F := T_1 \cap T_2$. Then 
    \begin{align*}
        \min\limits_{ c \in \bbR }
        \| u - c \|_{L^{p}(U)}
        &
        \leq 
        2 C_{\rm{EFNT},p}
        \max\left( 
            \frac{ \vol(T_1) }{ \vol(T_2) }
            ,
            \frac{ \vol(T_2) }{ \vol(T_1) }
        \right)^{\frac 1 p}
        \max\left( \diam(T_1), \diam(T_2) \right)
        \| \nabla u \|_{L^{p}(U)}
        \\&
        \leq 
        2 C_{\rm{EFNT},p}
        \left( 
            \frac{\diam(T_1)^n}{n! \vol(T_1)} 
            \frac{\diam(T_2)^n}{n! \vol(T_2)} 
        \right)^{\frac 1 p}
        \max\left( \diam(T_1), \diam(T_2) \right)
        \| \nabla u \|_{L^{p}(U)}
        .
    \end{align*}
    for any $u \in W^{1,p}(\Omega)$ with $p \in [1,\infty]$.
\end{lemma}

>>>>

\begin{remark}
    Our main interest in this manuscript are finite triangulations of compact sets. 
    There is another reason why we insist on the triangulation being finite: 
    if we do not require our simplicial complexes to be finite,
    then a reasonable definition of simplicial complex would need additional topological conditions. 
    % 
    For example, if we modify our definition of simplicial complex to be infinite, 
    then any subset of Euclidean space would give rise to an ``infinite $0$-dimensional complex''. But this obviously does not reflect the topology. 
    %
    A more interesting such example is this:
    the Cantor set $\calC \subseteq [0,1]$ is a compact set 
    that underlies an ``infinite $0$-dimensional simplicial complex''.
    If we place $\calC$ on the x-axis of a 2D coordinate system 
    and connect each member of $\calC$ to $(0,1)$ via a straight line segment, 
    then the resulting set is still compact, even path-connected,  
    but has an ``infinite $1$-dimensional triangulation''.
    % 
    However, none of these infinite families are infinite simplicial complexes in the sense of topology~\cite{spanier1966homology}. 
\end{remark}

@@

In the special case $p=2$, we always have $\| u - u_\Omega \|_{L^{2}(\Omega)} \leq \| u \|_{L^{2}(\Omega)}$ for any $v \in L^{2}(\Omega)$,
and therefore even $C_{\varnothing,\Omega,2} = C_{{\rm PF},\Omega,2}$. 
This follows from the orthogonality constant functions to average-free functions in $L^2(\Omega)$,
and it also follows from the projection estimate (see, e.g.,~\cite{xu2003some}).\footnote{\color{red}Is there a better name for this than Xu-Zikatanov estimate?}
Stern~\cite{stern2015banach} provided a generalization of the projection estimate that implies improved estimate for all $L^p$ spaces with $1 \leq p \leq \infty$:
since taking the average is a the projection onto the constants functions with unit norm, it now follows that 
\begin{align*}
    \| v - v_\Omega \|_{L^{p}(\Omega)}
    \leq 
    \min\left( 2, 2^{|2/p-1|} \right)
    \| v \|_{L^{p}(\Omega)}
    = 
    2^{|2/p-1|} 
    \| v \|_{L^{p}(\Omega)}
    ,
    \quad 
    v \in L^p(\Omega)
    .
\end{align*}
We have $1 \leq 2^{|2/p-1|} \leq 2$ for $1 \leq p \leq \infty$.
The upper bound is only attained in the limit cases $p = 1$ and $p = \infty$, and the lower bound is only attained if $p = 2$, which reproduces the improved estimate for the Hilbert space case.
The main consequence for us is the estimate 
$C_{\varnothing,\Omega,p} \leq 2^{|2/p-1|} C_{{\rm PF},\Omega,p}$.
We conclude that our notion of Poincar\'e--Friedrichs constant is equivalent to the notion of Poincar\'e constant in the literature, up to a numerical factor that only depends on $1 \leq p \leq \infty$.

There is yet another characterization of the Poincar\'e--Friedrichs inequality that we like to point out. 
We define the potential 
\begin{align*}
    \Phi( \bff ) := \argmin\limits_{ \substack{ v \in W^{1,p}(\Omega) \\ \nabla v = \bff } } \| v \|_{L^{p}(\Omega)},
    \quad 
    \bff \in \nabla W^{1,p}(\Omega)
    .
\end{align*}
Clearly, 
\begin{align*}
    \| \Phi(\bff) \|_{L^p(\Omega)} \leq C_{{\rm PF},\Omega,p} \| \bff \|_{L^p(\Omega)},
\end{align*}
and this inequality is sharp by definition of $\Phi$ provided that $C_{{\rm PF},\Omega,p}$ is smallest possible constant in \eqref{math:inequalitypf:gradient}. 
However, $\Phi : \nabla W^{1,p}(\Omega) \rightarrow L^p(\Omega)$ is generally a nonlinear operator for $p \neq 2$. 
Consequently, any \textit{linear} potential operator $\overline\Phi : \nabla W^{1,p}(\Omega) \rightarrow L^p(\Omega)$
satisfying $\nabla \overline\Phi( \bff ) = \bff$ for any $\bff \in \nabla W^{1,p}(\Omega)$ must have an operator norm that obeys the lower bound 
\begin{align*}
    C_{{\rm PF},\Omega,p} 
    \leq 
    \argmin\limits_{ v \in \nabla W^{1,p}(\Omega) \setminus \bbR } 
    \frac{ \| \overline\Phi(\nabla v) \|_{L^p(\Omega)} }{ \| \nabla v \|_{L^p(\Omega)} }
    .
\end{align*}
A natural choice is the linear operator $\Phi_{\varnothing} : \nabla W^{1,p}(\Omega) \rightarrow L^p(\Omega)$ that satisfies 
\begin{align*}
    \Phi_{\varnothing}( \nabla u ) = u - u_{\Omega},
    \quad 
    u \in W^{1,p}(\Omega)
    .
\end{align*}
Its operator norm is just the smallest Poincar\'e constant $C_{\varnothing,\Omega,p}$.

In the light of these musings, we clarify that our objective is the construction of linear potential operators for the gradient and later for the curl and divergence operators,
which is more specific than just proving an upper bound for the Poincar\'e--Friedrichs constant. 
Any Poincar\'e--Friedrichs inequality~\eqref{math:inequalitypf:gradient} is comparable to an upper bound for the generalized (possibly nonlinear) inverse of the gradient operator $\nabla : W^{1,p}(\Omega) \rightarrow L^{p}(\Omega)^{n}$. 
The potential reconstruction is the natural approach towards the topic when addressing the curl and divergence operators.

@@

We now collect examples for Poincar\'e--Friedrichs inequalities for important special cases; see also~\cite[Lemma~3.24]{ern2021finite} for a short overview. 
Over convex bounded domains, we have the Poincar\'e inequalities~\cite{bebendorf2003note,acosta2004optimal} 
\begin{align}\label{math:acostaduran}
    \| u - u_{\Omega} \|_{L^{1}(\Omega)}
    \leq 
    \frac{\diam(\Omega)}{2}
    \| \nabla u \|_{L^{1}(\Omega)}
    ,
    \quad 
    u \in W^{1,1}(\Omega)
    ,
    \\
    \| u - u_{\Omega} \|_{L^{2}(\Omega)} \label{math:bebendorf}
    \leq 
    \frac{\diam(\Omega)}{\pi}
    \| \nabla u \|_{L^{2}(\Omega)}
    ,
    \quad 
    u \in W^{1,2}(\Omega)
    .
\end{align}
These two estimates are the best possible in the cases $p=1$ and $p=2$, respectively, in terms of the diameter alone. 
Upper bounds for the Poincar\'e constant over convex domains with $1 < p < \infty$ are known in the literature~\cite{chua2006estimates}:
\begin{align}\label{math:chuawheeden}
    \| u - u_{\Omega} \|_{L^{p}(\Omega)}
    \leq 
    C_{{\rm CW},p}
    \diam(\Omega)
    \| \nabla u \|_{L^{p}(\Omega)}
    ,
    \quad 
    u \in W^{1,p}(\Omega)
    ,
\end{align}
where 
\begin{align}
    C_{{\rm CW},p} 
    := 
    \sup\limits_{ v \in C^\infty([0,1]) \setminus \bbR } 
    \frac{ 
        \| v - v_{[0,1]} \|_{L^{p}([0,1])} 
    }{ 
        \| \nabla v \|_{L^{p}([0,1])} 
    }
    \leq 
    \sqrt[p]{p} 2^{1-\frac 1 p}
    =
    2
    \left( \frac p 2 \right)^{\frac 1 p}
    .
\end{align}
The literature knows optimal Poincar\'e--Friedrichs constants over convex domains. 
According to~\cite{ferone2012remark,esposito2013poincare}, when $1 < p < \infty$, one can show that 
\begin{align}\label{math:esposito:pf}
    \min\limits_{ c \in \bbR }
    \| u - c \|_{L^{p}(\Omega)}
    \leq 
    C_{\rm{EFNT},p}
    \diam(\Omega)
    \| \nabla u \|_{L^{p}(\Omega)}
    ,
    \quad 
    u \in W^{1,p}(\Omega)
    ,
\end{align}
where $C_{\rm{EFNT},p}$ is the best possible constant that only depends on $p$ and equals 
\begin{align}
    C_{\rm{EFNT},p}
    :=
    \frac{ p \sin(\pi/p) }{ 2\pi \sqrt[p]{p-1} }
    .
\end{align}
Note that the last inequalities imply, again when $1 < p < \infty$, the Poincar\'e inequalities
\begin{align}\label{math:esposito:poincare}
    \| u - u_{\Omega} \|_{L^{p}(\Omega)}
    \leq 
    2^{|1-\frac 2 p|}C_{\rm{EFNT},p}
    \diam(\Omega)
    \| \nabla u \|_{L^{p}(\Omega)}
    ,
    \quad 
    u \in W^{1,p}(\Omega)
    .
\end{align}
The main feature in proving these results is that the best constant in the Poincar\'e inequality is already the constant in the $1$-dimensional case. 
Finally, since convex domains are Lipschitz domains: 
\begin{align}\label{math:lipschitzestimate}
    \min\limits_{ c \in \bbR }
    \| u - c \|_{L^{\infty}(\Omega)}
    \leq 
    \diam(\Omega)
    \| \nabla u \|_{L^{\infty}(\Omega)}
    ,
    \quad 
    u \in W^{1,\infty}(\Omega)
    .
\end{align}

@@

Given a gradient vector field, we can reconstruct the original scalar function up to a constant by a well-understood procedure: after fixing a starting point, we integrate the gradient vector field along lines emanating from that starting point. This defines a scalar potential. 
This shall be our inspiration for estimating the Poincar\'e constant over triangulated domains, which we achieve by an explicit construction of scalar potentials. 
After fixing a starting triangle, we construct a scalar potential for a given gradient vector field on larger and larger simplicial neighborhoods. This is achieved by a local patchwise construction of a potential and matching that local contribution to the global potential being constructed in intermediate steps. 
Consequently, the overall estimate depends on the local Poincar\'e constants, the mesh quality, and the depth of the recursion. 
\\

We achieve this goal via several auxiliary results. 
We start with a few geometric observations that pertain to the mesh regularity. 
Whenever $T$ is an $n$-dimensional simplex, we define the quantity 
\begin{align*}
    \mu(T)
    := 
    \frac{ \diam(T)^n }{ n! \vol(T) }
    .
\end{align*}
Moreover, when $\calT$ is an $n$-dimensional simplicial complex, we introduce 
\begin{align*}
    \mu(\calT) := \sup_{ T \in \subsimplex_{n}(\calT) } \mu(T),
    \qquad 
    \delta(\calT) := \sup_{ \substack{ T, T' \in \subsimplex_{n}(\calT) \\ T \cap T' \in \subsimplex_{n-1}(\calT) } } \frac{ \diam(T) }{ \diam(T') },
    \qquad 
    \kappa(\calT) := \sup_{ \substack{ T, T' \in \subsimplex_{n}(\calT) \\ T \cap T' \in \subsimplex_{n-1}(\calT) } } \frac{ \vol(T) }{ \vol(T') }.
\end{align*}

\begin{lemma}\label{lemma:affinetransform}
    Let $T$ be an $n$-simplex and let $\Psi : \Delta^n \rightarrow T$ be an affine diffeomorphism. Then 
    \begin{align*}
        \| \Jacobian \Psi \|
        \leq 
        \sqrt{n} \cdot \diam(T)
        ,
        \qquad 
        \| \Jacobian \Psi^{-1} \|
        \leq 
        \sqrt{2n^n} 
        % \frac{ n! \vol(T) } { \diam(T)^n }
        \mu(T)^{-1}
        \diam(T)^{-1}
        .
    \end{align*}
\end{lemma}
\begin{proof}
    We easily verify the first inequality. To prove the second inequality, let $\sigma_1 \geq \dots \geq \sigma_n \geq 0$ denote the singular values of $\Jacobian\Psi$ in descending order.
    Then $\sigma_1/\sigma_n \leq \sigma_1^n / \det(\Jacobian\Psi)$. Hence 
    \[
        \diam(T) 
        \leq 
        \sqrt{2} \sigma_1 
        \leq 
        \sqrt{2} 
        \frac{ \sigma_1^n }{ \det(\Jacobian\Psi) } 
        \sigma_n
        \leq 
        \sqrt{2n^n} 
        \frac{ \diam(T)^n }{ n! \vol(T) } 
        \sigma_n
        .
    \]
    The desired result is thus evident. 
\end{proof}

\begin{lemma}\label{lemma:volumecomparison}
    Let $T_1$ and $T_2$ be two $n$-simplices that share a common face $F$. Then 
    \begin{align*}
        \frac{ \vol(T_1) }{ \vol(T_2) }
        &\leq 
        \frac{\diam(T_1)^n}{n! \cdot \vol(T_1)} 
        \cdot 
        \frac{\diam(T_2)^n}{n! \vol(T_2)} 
        \leq 
        \mu(T_1) \mu(T_2)
        ,
        \\
        \diam(T_1)
        &\leq 
        \frac{ \diam(T_1)^n }{ n! \vol(T_1) }
        \diam(F)
        \leq 
        \mu(T_1)
        \diam(F)
        .
    \end{align*}
    If $\Xi : T_1 \rightarrow T_2$ is an affine diffeomorphism, then 
    \begin{align*}
        \| \Jacobian \Xi \|
        \leq 
        \sqrt{2n^{n+1}} 
        \frac{ \diam(T_1)^n }{ n! \vol(T_1) }
        \frac{ n! \vol(T_2) } { \diam(T_2)^n } 
        \leq 
        \sqrt{2n^{n+1}} 
        \frac{ \mu(T_1) }{ \mu(T_2) }
        .
    \end{align*}
\end{lemma}
\begin{proof}
    Let $h_1$ and $h_2$ be the heights of $F$ in the simplices $T_1$ and $T_2$, respectively. 
    Then $\vol(T_1) = h_1 \vol(F)/n!$ and $\vol(T_2) = h_2 \vol(F)/n!$, and thus $\vol(T_1)/\vol(T_2) = h_1/h_2$.
    We estimate 
    \begin{align*}
        h_1 &\leq \diam(T_1) \leq \frac{\diam(T_1)^n}{n! \cdot \vol(T_1)} \diam(F),
        \\
        h_2 &\geq n! \cdot \frac{\vol(T_2)}{\diam(T_2)^n} \diam(T_2) \geq n! \cdot \frac{\vol(T_2)}{\diam(T_2)^n} \diam(F)
        .
    \end{align*}
    The first estimate follows. 
    Let $h$ be the height of some face $F'$ other than $F$ in $T_1$. Then $h \leq \diam(F)$, and with similar arguments as before: 
    \begin{align*}
        \diam(F)
        \geq 
        h
        =
        n!
        \frac{ \vol(T_1) }{ \vol(F') }
        \geq 
        \frac{ n! \vol(T_1) }{ \diam(T_1)^n }
        \cdot 
        \diam(T_1)
        .
    \end{align*}
    That shows the second estimate. 
    Lastly, letting $\Xi : T_1 \rightarrow T_2$ be as above, we find 
    \begin{align*}
        \| \Jacobian \Xi \|
        &
        \leq 
        \sqrt{n} 
        \cdot 
        \diam(T_1)
        \sqrt{2n^n} 
        \frac{ n! \vol(T_2) } {\diam(T_2)^n } 
        \diam(T_2)^{-1}
        \\&
        \leq 
        \sqrt{n} 
        \frac{ \diam(T_1)^n }{ n! \vol(T_1) }
        \diam(F)
        \sqrt{2n^n} \frac{ n! \vol(T_2) } { \diam(T_2)^n } 
        \diam(F)^{-1}
        \leq 
        \sqrt{2n^{n+1}}
        \frac{ \diam(T_1)^n }{ n! \vol(T_1) }
        \frac{ n! \vol(T_2) } { \diam(T_2)^n } 
        .
    \end{align*}
    All the desired results thus follow. 
    % Together with analogous estimates that swap the roles of $h_1$ and $h_2$, we find 
    % \begin{align*}
    %     \max\left( \frac{h_1}{h_2}, \frac{h_2}{h_1} \right)
    %     \leq 
    %     \frac{\diam(T_1)^n}{n! \cdot \vol(T_1)} 
    %     \cdot 
    %     \frac{\diam(T_2)^n}{n! \vol(T_2)} 
    %     .
    % \end{align*}
\end{proof}

\begin{remark}
    % Whenever $T$ is an $n$-dimensional simplex, the ratio $\diam(T)^n / \vol(T)$ measures the ``shape quality'' of a simplex and is instance of a so-called \emph{shape measure}.
    % We can also rescale that by a factor of $1/n!$, as suggested from the above. 
    Whenever $T$ is an $n$-dimensional simplex, the ratio $\mu(T)$ measures the ``shape quality'' of a simplex and is instance of a so-called \emph{shape measure}.
    In our convention, the reference simplex has unit shape measure.
    This geometric ratio equals what is known as \emph{fatness} in differential geometry~\cite{cheeger1984curvature} and is precisely the reciprocal of the \emph{fullness} discussed by Whitney~\cite{whitney2012geometric}. 
    The \emph{thickness} of a simplex is the ratio of its smallest height to its diameter~\cite{munkres2016elementary}.
    Alternative shape measures have been used throughout the literature of numerical analysis and computational geometry to quantify the quality of simplices.
    One example, commonly referenced in finite element literature, is the ratio of the diameter and the radius of the largest inscribed circle of a simplex 
    (see~\cite[p.61, Definition 5.1]{braess2001finite}, ~\cite[p.97, Definition (4.2.16)]{brenner2008mathematical},~\cite[Definition~11.2]{ern2021finite}). 
\end{remark}

@@

\begin{lemma}\label{lemma:poincarefriedrichsoverfacepatch}
    Suppose that $T, T'$ are two $n$-simplices whose intersection is a common face $F := T_1 \cap T_2$. Then 
    \begin{align*}
        \min\limits_{ c \in \bbR }
        \| u - c \|_{L^{p}(U)}
        &
        \leq 
        2 C_{\rm{EFNT},p}
        \max\left( 
            \frac{ \vol(T_1) }{ \vol(T_2) }
            ,
            \frac{ \vol(T_2) }{ \vol(T_1) }
        \right)^{\frac 1 p}
        \max\left( \diam(T_1), \diam(T_2) \right)
        \| \nabla u \|_{L^{p}(U)}
        \\&
        \leq 
        2 C_{\rm{EFNT},p}
        \left( 
            \frac{\diam(T_1)^n}{n! \vol(T_1)} 
            \frac{\diam(T_2)^n}{n! \vol(T_2)} 
        \right)^{\frac 1 p}
        \max\left( \diam(T_1), \diam(T_2) \right)
        \| \nabla u \|_{L^{p}(U)}
        .
    \end{align*}
    for any $u \in W^{1,p}(\Omega)$ with $p \in [1,\infty]$.
\end{lemma}
\begin{proof}
    Let $\hat T_1$ be the $n$-simplex whose vertices $v_0=0, v_1=e_1, \dots, v_{n-1} = e_{n-1}, v_n = e_n$ are the origin and the $n$ canonical unit vectors. 
    We let $\hat T_2$ be the $n$-simplex whose vertices are $v_0=0, v_1=e_1, \dots, v_{n-1} = e_{n-1}, v'_n = -e_n$. 
    Write $U := T_1 \cup T_2$ and $\hat U := \hat T_1 \cup \hat T_2$.
    We fix affine homeomorphisms $\Phi_1 : \hat T_1 \rightarrow T_1$ and $\Phi_2 : \hat T_2 \rightarrow T_2$
    which map the convex closure of $v_0, \dots, v_{n-1}$ onto the common face $F$.
    Note that these affine transformations define a bi-Lipschitz mapping $\Phi : \hat U \rightarrow U$.
